Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-15 paper/main.tex
analysis: explain design matrices

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events [lenght = 20 ms?].\todo{actually, that might not be
true}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since the time-series of modeled hemodynamic activity were based on events in
stimuli that were not designed for research, we then tested if time-series were
correlated (i.e. share variance) leading to low detection power in subsequent
analyses\todo{pick your favorite}.
% fixed time course; detection power
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Since we annotated events in fixed time courses that could not experimentally
manipulated, the modeled time-series [of hemodynamic activity] based on these
events could be correlated leading to shared variance and thus low detection
power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
\texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749). This was
expected and served as ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
\label{fig:reg-corr}
\end{figure*}

@@

\todo[inline]{regressors of other stimulus in GLM of other stimulus}
% categories taken from movie cut annotation
Maybe only say in table caption: To create contrasts of cross-modal negative
control and to capture variance of a possibly confounding change of the
soundscape after a cut, we also implemented the five movie cut-related
regressors used in the GLM of the AV stimulus (see details below) in the model
of the AD stimulus.

% contrasts
Based on these regressors, we then created $t$-contrasts that we presumed to
subtract variance correlating with the perception of non-spatial information
from variance correlating with the perception of spatial information.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ingredients" to answer our questions (cf. intro); we have annotations; define
% congruent contrasts based on regressors based on annotations

% repeat key question (cf. end of intro)
The key question of the current study was if a) we could operationalize the
perceptual processes in an audio-visual and exclusively auditory
naturalistic stimulus and if b) contrasting that fcompared to an
operationalization of non-spatial perception  would yield to increased
hemodynamic activity in the PPA as defined by a visual localizer experiment.
% difference (kinda repetition)
Instead of carefully selecting and designing conceptualized/simplified stimuli
that we assumed to match the proposed perceptual processes, we selected and
categorized stimulus features (movie cuts and spoken nouns) that are embedded in
two naturalistic stimuli.

@@

\todo[inline]{I created the part "design matrix" cause following parts are
usually written in the "regressor paragraph" in publications but do not really
fit in the subsection above}

\todo[inline]{SE: gab es ein separates null-event für jeden zeitraum zwischen
zwei annotierten events oder war das ein regressor der immer wieder kam?}

% null regressors
If a stimulus segment did not contain an event of a category (e.g. no event of
\texttt{vpe\_old} in segment 3 of the movie; cf. Table \ref{tab:ao-events}), a
null regressor was chosen for that category in that segment.

% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

\subsubsection{Contrasts}

% intro
To test the robustness of our approach, we operationalized the
perception of spatial information compared to the perception of ``non-spatial''
information differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).\todo{make ref to what is no "Audio-description: annotation"}
% thus: primary contrasts
For each stimulus, we chose one contrast to be ``primary contrast'' for further
inspection and a detailed report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.

@@

% AV primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus objects or faces.\todo{syntax?}

@@

\paragraph{control contrasts: AD \& AV}

@@

To test our model, we ran several $t$-contrasts as part of a GLM for each
stimulus.

% intro
Similarly to the reviewed studies that employed simplified stimuli, we conducted
a standard two-level general linear model (GLM) analysis to create
subject-specific results ($Z$-maps) across the 8 segments for every subject. A
subsequent, third-level analysis averaged contrast estimates over subjects.

>>>>

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events.\todo{actually, it was a box car of 200 ms after
starting with the cut}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
\texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749). This was
expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
\label{fig:reg-corr}
\end{figure*}

@@

% level 1 and 2; similarly to the reviewed studies that employed designed
% stimuli; we "based on stimulus annotations"
We then tested our modeled hemodynamic responses by conducting standard
two-level general linear model (GLM) analyses to create subject-specific results
($Z$-maps) across the 8 segments for every subject and each stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

@@

% AV design matrix
For the first level analysis of the AV stimulus, the modeled hemodynamic
responses related to all movie cuts (including \texttt{no\_cut}) and six
low-level perceptual confounds were included as regressors in the design matrix
(s. Table \ref{tab:av-events}).
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included (s. Table \ref{tab:ao-events}).
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to cue switches to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus [and to capture variance of a possibly confounding change of the
soundscape after a cut], we implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
In analyses of both stimuli, a null regressor was chosen for a event category in
a segment, if that segment did not contain an event of the category (e.g. no
event of \texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

\paragraph{PPA Contrasts} \todo{maybe repeat key questions (cf. intro) here}

% intro
To test the robustness of our approach, we then operationalized the
perception of spatial information compared to the perception of ``non-spatial''
information differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).\todo{make ref to what is no "Audio-description: annotation"}
% thus: primary contrasts
For each stimulus, we chose one contrast to be ``primary contrast'' for further
inspection and a detailed report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.

% AV primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or
faces.

@@

@@

\paragraph{Control contrasts}

@@
